### 2020-03-06 Draft_V6.tex

\documentclass[12pt,a4paper,hyperref]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins}
\usepackage[colorlinks,
            linkcolor=ultramarine,
            anchorcolor=green,
            citecolor=darkblue
            ]{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
\usepackage{hyperref}
\newtheorem{myDef}{Definition}
\newtheorem{myTheo}{Theorem}
\newtheorem{myProp}{proposition}
\newtheorem{myRem}{Remark}
\newtheorem{myAssu}{Assumption}
\newtheorem{myCor}{Corollary}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

@@

\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\floatpagefraction}{0.60}
\renewcommand{\appendixpagename}{\Large Appendix}
\setcounter{secnumdepth}{3}
\begin{document}
\begin{titlepage}

@@

\HRule \\[0.4cm]
{ \huge \bfseries Dynamic Heterogeneous Panels with multi-factor error sructure}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

@@

\section{Dynamic heterogeneous panel data model with multifactor error structure}
Reconsider model $(\ref{1})$ here,
\begin{align}
\begin{split}
y^{b}_{i,t}&=\phi_{i} y^{b}_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u^{b}_{i,t}  \\
&= \boldsymbol{w}^{b'}_{i,t}\boldsymbol{\theta}_{i}+u^{b}_{i,t}, \,\,\,\, \,\, \,\, \,\,\,\, \,\,\,\, \,\,\,\, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \label{m1}
\end{split}
\end{align}
with
\begin{align}
u^{b}_{i,t}=\boldsymbol{\gamma}^{'}_{y,i}\boldsymbol{f}_{y,t}+\varepsilon_{i,t}, 
\end{align}
where $\boldsymbol{\gamma}_{y,i}$ is a $m_{y} \times 1$ vector of unobservable factors and $\boldsymbol{f}_{y,t}$ is a $m_{x} \times 1$ vector of factor loading and $\varepsilon_{i,t}$ is an idiosyncratic error. 
Regressor $\boldsymbol{x}_{i,t}$ follow the process as 
\begin{align}
 \boldsymbol{x}_{i,t}=\boldsymbol{\Gamma}^{'}_{x,i}\boldsymbol{f}_{x,t}+ \boldsymbol{v}_{i,t}.
\end{align}
Again, we stack the $T$ observations for each $i$ as
\begin{align}
\boldsymbol{y}_{i}= \phi_{i} \boldsymbol{y}_{i}+\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+\boldsymbol{u}_{i}\,\,\,\, with\,\,\boldsymbol{u}_{i}=\boldsymbol{F}_{y}\boldsymbol{\gamma}_{y,i}+\boldsymbol{\varepsilon}_{i},
\end{align}
where $\boldsymbol{F}_{y}=\left( \boldsymbol{f}_{y,1}, \boldsymbol{f}_{y,2},\ldots,\boldsymbol{f}_{y,T}  \right)^{'}$ and $\boldsymbol{\varepsilon}_{i}=\left( \varepsilon_{i,1}, \varepsilon_{i,2},\ldots,\varepsilon_{i,T} \right)^{'}$. And the regressor $\boldsymbol{X}_{i}$ as
\begin{align}
\boldsymbol{X}_{i}=\boldsymbol{F}_{x}\boldsymbol{\Gamma}_{x,i}+\boldsymbol{V}_{i},
\end{align}
where $\boldsymbol{F}_{x}=\left( \boldsymbol{f}_{x,1}, \boldsymbol{f}_{x,1},\ldots,\boldsymbol{f}_{x,T} \right)^{'}$ and $\boldsymbol{V}_{i}=\left( \boldsymbol{v}_{i,1}, \boldsymbol{v}_{i,2},\ldots,\boldsymbol{v}_{i,T}.  \right)$
Follow \citet{bai:2003} and \citet{bai:2009}, we can use principal components approach to estimate $\boldsymbol{F}_{x}$ and $\boldsymbol{F}_{x,-1}$. Then, we can build the projection matrices as
\begin{align}
\boldsymbol{M}_{\hat{F}_{x}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x}\left(\hat{\boldsymbol{F}}^{'}_{x} \hat{\boldsymbol{F}}_{x}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x}; \,\, \boldsymbol{M}_{\hat{F}_{x,-1}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x,-1}\left(\hat{\boldsymbol{F}}^{'}_{x,-1} \hat{\boldsymbol{F}}_{x,-1}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x,-1}.
\end{align}
Then, we can project out factor structure in $\boldsymbol{X}_{i}$.  Premultiplying $\boldsymbol{X}_{i}$ by $\boldsymbol{M}_{\hat{F}_{x}}$, we have $\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}=\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{V}_{i}.$ And we assume $\boldsymbol{V}_{i}$ is independent of $\boldsymbol{\varepsilon}$, $\boldsymbol{F}_{x}$, $\boldsymbol{F}_{y}$ and $\boldsymbol{\gamma}_{y,i}$. Then, we can see that $E\left(\boldsymbol{X}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{u}_{i} \right)=E\left(  \boldsymbol{V}_{i}^{'}\boldsymbol{M}_{F_{x}}\boldsymbol{u}_{i} \right).$
Therefore, using the similar approach in section $1$, we can collect the set of instrumental variables:
\begin{align}
\boldsymbol{Z}_{i}=\left( \boldsymbol{M}_{F_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{F_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{F_{x,-j}}\boldsymbol{X}_{i,-j}, \right)
\end{align}
Define $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}^{(j)}_{i}=\boldsymbol{Z}^{(j)}_{i} \left(\boldsymbol{Z}^{(j)'}_{i}\boldsymbol{Z}^{(j)}_{i} \right)^{-1}\boldsymbol{Z}^{(j)'}_{i}
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $1\leq j \leq J$ with $J$ is the maximum lags of variables that we can observe.

Then, we can show 2SLS estimator of $\boldsymbol{\theta}_{i}$ :
\begin{align}
\hat{\boldsymbol{\theta}}_{i}= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{W}^{b}_{i} \right)^{-1} \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i} \boldsymbol{y}_{i},
\end{align}

@@

Therefore, we have mean average 2SLS estimator, $\hat{\boldsymbol{\theta}}^{b}_{i}$ ,as
\begin{align}
\hat{\boldsymbol{\theta}}^{\ast b}_{i}= \left( \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}^{b}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{b'}_{i}\boldsymbol{P}^{b}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}^{b}_{i}.
\end{align}

@@

\newpage
\appendix
\appendixpage
\section{Asymptotic property of LS estimator}

>>>>

\documentclass[12pt,a4paper,hyperref]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
	\definecolor{ultramarine}{rgb}{0.07, 0.04, 0.56}
\usepackage{amsmath, natbib, latexsym, array, amssymb,longtable,float, graphicx, appendix,lscape,diagbox,textcomp,placeins,mathtools}
\usepackage[colorlinks,
            linkcolor=ultramarine,
            anchorcolor=green,
            citecolor=darkblue
            ]{hyperref}
\usepackage[flushleft]{threeparttable}
\usepackage[top=2.7cm, left=3cm, right=3cm, bottom=2.7cm]{geometry}
\usepackage{hyperref}
\newtheorem{myDef}{Definition}
\newtheorem{myTheo}{Theorem}
\newtheorem{myProp}{proposition}
\newtheorem{myRem}{Remark}
\newtheorem{myAssu}{Assumption}
\newtheorem{myCor}{Corollary}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

@@

\newenvironment{sequation}{\begin{equation}\tiny}{\end{equation}}
\DeclareMathOperator*{\plim}{plim}
\renewcommand{\floatpagefraction}{0.60}
\renewcommand{\appendixpagename}{\Large Appendix}
\setcounter{secnumdepth}{3}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\makeatletter
\let\oldabs\abs
\begin{document}
\begin{titlepage}

@@

\HRule \\[0.4cm]
{ \huge \bfseries Model Average of Dynamic Heterogeneous Panels with multi-factor error sructure}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]

@@

\section{Dynamic heterogeneous panel data model with multifactor error structure}
Reconsider model $(\ref{1})$ here,
\begin{align}
\begin{split}
y^{b}_{i,t}&=\phi_{i} y^{b}_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u^{b}_{i,t}  \\
&= \boldsymbol{w}^{b'}_{i,t}\boldsymbol{\theta}_{i}+u^{b}_{i,t}, \,\,\,\, \,\, \,\, \,\,\,\, \,\,\,\, \,\,\,\, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \label{m1}
\end{split}
\end{align}
with
\begin{align}
u^{b}_{i,t}=\boldsymbol{\gamma}^{'}_{y,i}\boldsymbol{f}_{y,t}+\varepsilon_{i,t},
\end{align}
where $\boldsymbol{\gamma}_{y,i}$ is a $m_{y} \times 1$ vector of unobservable factors and $\boldsymbol{f}_{y,t}$ is a $m_{x} \times 1$ vector of factor loading and $\varepsilon_{i,t}$ is an idiosyncratic error.
Regressor $\boldsymbol{x}_{i,t}$ follow the process as
\begin{align}
 \boldsymbol{x}_{i,t}=\boldsymbol{\Gamma}^{'}_{x,i}\boldsymbol{f}_{x,t}+ \boldsymbol{v}_{i,t}.
\end{align}
Again, we stack the $T$ observations for each $i$ as
\begin{align}
\boldsymbol{y}_{i}= \phi_{i} \boldsymbol{y}_{i}+\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+\boldsymbol{u}_{i}\,\,\,\, with\,\,\boldsymbol{u}_{i}=\boldsymbol{F}_{y}\boldsymbol{\gamma}_{y,i}+\boldsymbol{\varepsilon}_{i},
\end{align}
where $\boldsymbol{F}_{y}=\left( \boldsymbol{f}_{y,1}, \boldsymbol{f}_{y,2},\ldots,\boldsymbol{f}_{y,T}  \right)^{'}$ and $\boldsymbol{\varepsilon}_{i}=\left( \varepsilon_{i,1}, \varepsilon_{i,2},\ldots,\varepsilon_{i,T} \right)^{'}$. And the regressor $\boldsymbol{X}_{i}$ as
\begin{align}
\boldsymbol{X}_{i}=\boldsymbol{F}_{x}\boldsymbol{\Gamma}_{x,i}+\boldsymbol{V}_{i},
\end{align}
where $\boldsymbol{F}_{x}=\left( \boldsymbol{f}_{x,1}, \boldsymbol{f}_{x,1},\ldots,\boldsymbol{f}_{x,T} \right)^{'}$ and $\boldsymbol{V}_{i}=\left( \boldsymbol{v}_{i,1}, \boldsymbol{v}_{i,2},\ldots,\boldsymbol{v}_{i,T}.  \right)$
Follow \citet{bai:2003} and \citet{bai:2009}, we can use principal components approach to estimate $\boldsymbol{F}_{x}$ and $\boldsymbol{F}_{x,-1}$. Then, we can build the projection matrices as
\begin{align}
\boldsymbol{M}_{\hat{F}_{x}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x}\left(\hat{\boldsymbol{F}}^{'}_{x} \hat{\boldsymbol{F}}_{x}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x}; \,\, \boldsymbol{M}_{\hat{F}_{x,-1}}=\boldsymbol{I}_{T}-\hat{\boldsymbol{F}}_{x,-1}\left(\hat{\boldsymbol{F}}^{'}_{x,-1} \hat{\boldsymbol{F}}_{x,-1}   \right)^{-1}\hat{\boldsymbol{F}}^{'}_{x,-1}.
\end{align}
Then, we can project out factor structure in $\boldsymbol{X}_{i}$.  Premultiplying $\boldsymbol{X}_{i}$ by $\boldsymbol{M}_{\hat{F}_{x}}$, we have $\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}=\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{V}_{i}.$ And we assume $\boldsymbol{V}_{i}$ is independent of $\boldsymbol{\varepsilon}$, $\boldsymbol{F}_{x}$, $\boldsymbol{F}_{y}$ and $\boldsymbol{\gamma}_{y,i}$. Then, we can see that $E\left(\boldsymbol{X}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{u}_{i} \right)=E\left(  \boldsymbol{V}_{i}^{'}\boldsymbol{M}_{F_{x}}\boldsymbol{u}_{i} \right).$
Therefore, using the similar approach in section $1$, we can collect the set of instrumental variables:
\begin{align}
\hat{\boldsymbol{Z}}^{j}_{i}=\left( \boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{\hat{F}_{x,-j}}\boldsymbol{X}_{i,-j}, \right)
\end{align}
Define $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}^{(j)}_{i}=\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\hat{\boldsymbol{Z}}^{(j)'}_{i}
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $1\leq j \leq J$ with $J$ is the maximum lags of variables that we can observe.

Then, we can show 2SLS estimator of $\boldsymbol{\theta}_{i}$ :
\begin{align}
\hat{\boldsymbol{\theta}}_{i}= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{P}^{(j)}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{W}_{i} \right)^{-1} \boldsymbol{W}^{'}_{i}\boldsymbol{P}^{(j)}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{y}_{i},
\end{align}

@@

Therefore, we have mean average 2SLS estimator, $\hat{\boldsymbol{\theta}}^{b}_{i}$ ,as
\begin{align}
\hat{\boldsymbol{\theta}}^{\ast }_{i}= \left( \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right)\tilde{\boldsymbol{W}}_{i} \right)^{-1} \tilde{\boldsymbol{W}}^{'}_{i}\boldsymbol{P}_{i}\left(\boldsymbol{\omega^{(i)\ast}} \right) \tilde{\boldsymbol{y}}_{i}.
\end{align}

@@

\newpage
\appendix
\appendixpage
\section{Consistency of model average IV estimator}
First we consider IV estimator without model average. From previous section, IV estimator can be written as 
\begin{align}
\begin{split}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{i}-\boldsymbol{\theta}_{i}\right)&= \left( \boldsymbol{W}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{W}_{i} \right)^{-1} \times \\ &\boldsymbol{W}^{'}_{i}\hat{\boldsymbol{Z}}^{(j)}_{i} \left(\hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}}\hat{\boldsymbol{Z}}^{(j)}_{i} \right)^{-1}\left( T^{-1/2} \hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}\right),
\end{split}
\end{align}
When $N,T \to \infty$, we can show $T^{-1/2} \hat{\boldsymbol{Z}}^{(j)'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}$ is $O_{p}\left(1 \right)$ as following.
Consider the first element of $\hat{\boldsymbol{Z}}^{(j)}_{i}=\left( \boldsymbol{M}_{\hat{F}_{x}}\boldsymbol{X}_{i}, \boldsymbol{M}_{\hat{F}_{x,-1}}\boldsymbol{X}_{i,-1},\ldots  ,\boldsymbol{M}_{\hat{F}_{x,-j}}\boldsymbol{X}_{i,-j} \right).$ Then we have 
\begin{align}
T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i}\boldsymbol{M}_{\hat{F}_{x}} \boldsymbol{u}_{i}= T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i}\boldsymbol{M}_{\hat{F}^{0}_{x}} \boldsymbol{u}_{i}+T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left(\boldsymbol{M}_{\hat{F}_{x}} -\boldsymbol{M}_{\hat{F}^{0}_{x}} \right) \boldsymbol{u}_{i}.
\end{align}

\begin{align}
\begin{split}
&T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left(\boldsymbol{M}_{\hat{F}_{x}}-\boldsymbol{M}_{\hat{F}^{0}_{x}} \right) \boldsymbol{u}_{i}= -T^{-1/2} \hat{\boldsymbol{X}}^{'}_{i} \left( \frac{\hat{\boldsymbol{F}}^{'}_{x}\hat{\boldsymbol{F}}_{x}  }{T} -\boldsymbol{P}_{F^{0}_{x}}  \right) \boldsymbol{u}_{i}= \\
&  -T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}\boldsymbol{G}^{'}_{x}\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}-T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x} \boldsymbol{G}_{x}  \right)}{T}\left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i} \\
& -T^{-1/2} \frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}\boldsymbol{G}_{x} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}-T^{-1/2} \frac{\boldsymbol{X}^{'}_{i} \boldsymbol{F}^{0}_{x}}{T} \left( \boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left( \frac{\boldsymbol{F}^{0'}_{x} \boldsymbol{F}^{0}_{x} }{T} \right)^{-1}      \right)\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i} \\
&= -\left( b_{1}+ b_{2}+b_{3}+b_{4} \right).
\end{split}
\end{align}
By Cauchy–Schwarz inequality we know

\begin{align}
\begin{split}
&\abs{b_{1}}\leq T^{1/2} \norm{\frac{ \boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right) }{T}} \norm{\boldsymbol{G}_{x}}\norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T}}\leq T^{1/2} \norm{\boldsymbol{\Gamma}_{x,i}}\norm{\frac{\boldsymbol{F}^{'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}}\norm{\boldsymbol{G}_{x}} \norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}}}\norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}\\
&+T^{1/2} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G} \right)}{T} } \norm{\boldsymbol{G}_{x}}\norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}}} \norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}=\sqrt{T}O_{p}\left(c^{-2}_{NT} \right),
\end{split}
\end{align}
where $\norm{\frac{\boldsymbol{F}^{0'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right) }{T}}= O_{p}\left(c^{-2}_{NT}\right)$, $\norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G} \right)}{T} }=  O_{p}\left(c^{-2}_{NT}\right)$, $ \norm{\boldsymbol{G}_{x}}=  O_{p}\left(c^{-2}_{NT}\right)$, $\norm{\boldsymbol{\Gamma}_{x,i}}=  O_{p}\left(c^{-2}_{NT}\right)$, $\frac{ \norm{\boldsymbol{F}^{0}_{x}}}{\sqrt{T}}=  O_{p}\left(c^{-2}_{NT}\right)$, $ \norm{\frac{\boldsymbol{u}_{i}}{\sqrt{T}}}\leq \norm{\boldsymbol{\gamma^{0}_{i}}} \frac{\norm{\boldsymbol{F}^{0}_{y}}}{\sqrt{T}}+\norm{\boldsymbol{\lambda}^{0}_{i}} \frac{ \norm{\boldsymbol{F}^{0}_{y}} }{\sqrt{T}}+ \frac{\norm{\varepsilon_{i} } }{\sqrt{T}}=O_{p}\left(c^{-2}_{NT}\right).$

\begin{align}
\begin{split}
\abs{b_{2}}&\leq \sqrt{T} \norm{\frac{\boldsymbol{X}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}}{T} } \\
& \leq \sqrt{T} \norm{\Gamma_{x,i}} \norm{\frac{\boldsymbol{F}^{'}_{x}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}\boldsymbol{u}_{i}}{T}}+ \\
&\sqrt{T}  \norm{\Gamma_{x,i}} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} \norm{\frac{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}\boldsymbol{u}_{i}}{T}}= \sqrt{T}O_{p}\left( c^{-2}_{NT} \right),
\end{split}
\end{align}
where $\norm{\frac{\boldsymbol{u}^{'}_{i} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)^{'}}{T}} \leq \norm{\boldsymbol{\gamma}^{0}_{i}} \norm{\frac{\boldsymbol{V}^{'}_{i}\left(\hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x} \right)}{T}} + \norm{\boldsymbol{\lambda}^{0}_{i}} \norm{\frac{\boldsymbol{F}^{0'}_{y} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}}+ \norm{\frac{\boldsymbol{\varepsilon}^{'}_{i} \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}  \right)}{T}} $

\begin{align}
\begin{split}
\abs{b_{3}}&\leq  \sqrt{T} \norm{\frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}} \norm{\boldsymbol{G}_{x} } \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i} } \\
&\leq \sqrt{T} \norm{\boldsymbol{\Gamma}_{x,i}} \norm{\frac{\boldsymbol{F}^{'}_{x}\boldsymbol{F}_{x}}{T}} \norm{\boldsymbol{G}_{x}} \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}} +\\
&\sqrt{T} \norm{ \frac{\boldsymbol{V}_{i}}{\sqrt{T}} } \norm{\frac{\boldsymbol{F}^{0}_{x}}{\sqrt{T}} } \norm{\boldsymbol{G}_{x}} \norm{ \left( \hat{\boldsymbol{F}}_{x}-\boldsymbol{F}^{0}_{x}\boldsymbol{G}_{x}   \right)^{'}\boldsymbol{u}_{i}}=\sqrt{T}O_{p}\left( c^{-2}_{NT} \right).
\end{split}
\end{align}

\begin{align}
\begin{split}
\abs{b_{4}}&\leq   \sqrt{T}\norm{\frac{\boldsymbol{X}^{'}_{i}\boldsymbol{F}^{0}_{x} }{T}}  \norm{\boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left(\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}}{T}  \right)^{-1} }\norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T}} \\
& \sqrt{T} \norm{\boldsymbol{G}_{x} } \norm{\frac{\boldsymbol{F}^{'}_{x}\boldsymbol{F}_{x}}{T}}  \norm{\boldsymbol{G}_{x}\boldsymbol{G}^{'}_{x}-\left(\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{F}^{0}_{x}}{T}  \right)^{-1} } \norm{\frac{\boldsymbol{F}^{0'}_{x}\boldsymbol{u}_{i}}{T} }=\sqrt{T}O_{p}\left( c^{-2}_{NT} \right).
\end{split}
\end{align}
